### 2017-01-07 paper/evaluation.tex
Added new plots

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we run
the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).
To avoid noise from OS events, we executed this experiment in our
dedicated server remotely via SSH with the operating system running
only essential services (\eg, the SSH server). \Fix{Describe CPU
isolation}.

@@

We grouped the subjects according the execution time (in average)
using the same criteria of a previous work
\cite{gligoric-etal-issta2015}: subjects that run in less than one
minute were classified as \emph{short execution} and \emph{long
execution} otherwise. Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group and figure~\ref{fig:boxplots-time}
shows the distribution of elapsed time for each group (boxplots).

\begin{figure}[h!]
    \centering
    \begin{minipage}{2in}%
    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$) and long
    execution ($1m \leq t$).}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{minipage}{2.5in}%
    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:boxplots-time} Distribution of time execution
    per group. Outliers from \emph{Long} are ignored for better
    readability.}
\end{figure}

Results indicate that a relatively high number of projects from the
sample set (\ie, 29,2\%) requires at least five minutes to execute.
The boxplot for the \emph{long} group reveals \Fix{dissect the
boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
group}.  It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision.

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we \Fix{describe CPU isolation with Kernel
settings}.

@@

%% We grouped the subjects according the execution time (in average)
%% using the same criteria of a previous work
%% \cite{gligoric-etal-issta2015}: subjects that run in less than one
%% minute were classified as \emph{short execution} and \emph{long
%% execution} otherwise. Figure~\ref{fig:piechart-time} shows the
%% proportion of subjects per group and figure~\ref{fig:boxplots-time}
%% shows the distribution of elapsed time for each group (boxplots).
%%

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.21\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}

    \end{subfigure}
    \caption{Caption place holder}
\end{figure}

%% Results indicate that a relatively high number of projects from the
%% sample set (\ie, 29,2\%) requires at least five minutes to execute.
%% The boxplot for the \emph{long} group reveals \Fix{dissect the
%% boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
%% group}.  It is important to mention that
%% Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
%% time: some tests may finish early due to a failure since the subjects
%% were tested in a potentially unstable revision.
